Code used to generate paper results : Database comparison and CT characteristics

### 2023-10-19 Paper_code-Database_CT.Rmd
Added description of lost genes

```{r CTdatabase_ours}
CTdatabase_ours <- Venn(list(CTdatabase = CTdatabase_cleaned$external_gene_name,
                             CTexploreR = CT_genes$external_gene_name))
plot(CTdatabase_ours)
```

## CTexploreR VS omics databases

```{r upset_plot}
core_ours <- Venn(list(Jamin = Jamin_core_CT$Gene, 
                       CTexploreR = CT_genes$external_gene_name))

@@

Carter_ours <- Venn(list(Carter_CT = Carter_CT$Gene_Name, 
                         CTexploreR = CT_genes$external_gene_name))

gene_list <- list(Jamin = Jamin_core_CT$Gene, 
                  CTdatabase = CTdatabase_cleaned$external_gene_name, 
                  CTatlas = Wang_CT$external_gene_name, 
                  CTexploreR = CT_genes$external_gene_name, 
                  Carter = Carter_CT$Gene_Name)

@@

@@

@@

@@

@@

@@

>>>>

```{r CTdatabase_ours}
CTdatabase_ours <- Venn(list(CTdatabase = CTdatabase_cleaned$external_gene_name,
                             CTexploreR = CT_genes$external_gene_name))
gp <- VennThemes(compute.Venn(CTdatabase_ours))
gp[["Face"]][["11"]]$fill <-  "mistyrose"
gp[["Face"]][["01"]]$fill <-  "darkseagreen1"
gp[["Face"]][["10"]]$fill <-  "lightsteelblue1"
gp[["Set"]][["Set1"]]$col <-  "paleturquoise4"
gp[["Set"]][["Set2"]]$col <-  "darkseagreen4"
gp[["SetText"]][["Set1"]]$col <-  "paleturquoise4"
gp[["SetText"]][["Set2"]]$col <-  "darkseagreen4"
plot(CTdatabase_ours, gp = gp)

Lost genes analysis

```{r CTdatabase_lost}
CTdatabase_lost <- all_genes %>%
  filter(external_gene_name %in% CTdatabase_ours@IntersectionSets[["10"]])

# 10 Genes are lost because not in any  database

CTdatabase_lost[is.na(CTdatabase_lost$testis_specificity), ]$testis_specificity <- "not_specific"
table(CTdatabase_lost$testis_specificity)

table(CTdatabase_lost$testis_cell_type)

table(CTdatabase_lost$Higher_in_somatic_cell_type)

table(CTdatabase_lost$TCGA_category)

table(CTdatabase_lost$CCLE_category)
```

## CTexploreR VS omics databases
```{r upset_plot}
core_ours <- Venn(list(Jamin = Jamin_core_CT$Gene, 
                       CTexploreR = CT_genes$external_gene_name))

@@

Carter_ours <- Venn(list(Carter_CT = Carter_CT$Gene_Name, 
                         CTexploreR = CT_genes$external_gene_name))
gene_list <- list(Jamin = Jamin_core_CT$Gene, 
                  CTdatabase = CTdatabase_cleaned$external_gene_name, 
                  CTatlas = Wang_CT$external_gene_name, 
                  CTexploreR = CT_genes$external_gene_name, 
                  Carter = Carter_CT$Gene_Name)

@@

Lost genes analysis

```{r Jamin_lost}
Jamin_lost <- all_genes %>%
  filter(external_gene_name %in% core_ours@IntersectionSets[["10"]])

Jamin_lost[is.na(Jamin_lost$testis_specificity), ]$testis_specificity <- "not_specific"
table(Jamin_lost$testis_specificity)

table(Jamin_lost$testis_cell_type)

table(Jamin_lost$Higher_in_somatic_cell_type)

table(Jamin_lost$TCGA_category)

table(Jamin_lost$CCLE_category)
```

```{r Wang_lost}
Wang_lost <- all_genes %>%
  filter(external_gene_name %in% Wang_ours@IntersectionSets[["10"]])

Wang_lost[is.na(Wang_lost$testis_specificity), ]$testis_specificity <- "not_specific"
table(Wang_lost$testis_specificity)

table(Wang_lost$testis_cell_type)

table(Wang_lost$Higher_in_somatic_cell_type)

table(Wang_lost$TCGA_category)

table(Wang_lost$CCLE_category)

```{r Carter_lost}
Carter_lost <- all_genes %>%
  filter(external_gene_name %in% Carter_ours@IntersectionSets[["10"]])

Carter_lost[is.na(Carter_lost$testis_specificity), ]$testis_specificity <- "not_specific"
table(Carter_lost$testis_specificity)

table(Carter_lost$testis_cell_type)

table(Carter_lost$Higher_in_somatic_cell_type)

table(Carter_lost$TCGA_category)

table(Carter_lost$CCLE_category)
```

@@

GTEX_expression(not_specific$external_gene_name, units = "log_TPM")

@@

testis_expression(somatic_testis$external_gene_name)

@@

HPA_cell_type_expression(somatic_tissue$external_gene_name)

@@

TCGA_expression(not_TCGA_activated$external_gene_name,
                tumor = "all",
                units = "log_TPM")

@@

CCLE_expression(not_CCLE_activated$external_gene_name,
                  type = c("lung", "skin", "colorectal",
                           "gastric", "breast", "head_and_neck"),
                units = "log_TPM")
